Our Rodent Species

### 2017-09-27 profiles.Rmd

>>>>

  Rodents = c("![](rodent_pictures/color_pictures/BA.png)",
              "![](rodent_pictures/color_pictures/PB.png)",
              "![](rodent_pictures/color_pictures/PH.png)",
              "![](rodent_pictures/color_pictures/PI.png)",
              "![](rodent_pictures/color_pictures/PP.png)",
              "![](rodent_pictures/color_pictures/DM.png)",
              "![](rodent_pictures/color_pictures/DO.png)",
              "![](rodent_pictures/color_pictures/DS.png)",
              "![](rodent_pictures/Rodent_silhouettes/5-White-throatedwoodrat.png)",
              "![](rodent_pictures/Rodent_silhouettes/6-NorthernGrasshoppermouse.png)",
              "![](rodent_pictures/Rodent_silhouettes/7-SouthernGrasshoppermouse.png)",
              "![](rodent_pictures/color_pictures/PF.png)",
              "![](rodent_pictures/color_pictures/PE.png)",
              "![](rodent_pictures/color_pictures/PL.png)",
              "![](rodent_pictures/color_pictures/PM.png)",
              "![](rodent_pictures/Rodent_silhouettes/16-Fulvouseharvestmouse.png)",
              "![](rodent_pictures/Rodent_silhouettes/17-WesternHarvestmouse.png)",
              "![](rodent_pictures/Rodent_silhouettes/18-Plainsharvestmouse.png)",
              "![](rodent_pictures/Rodent_silhouettes/19-Tawny-belliedcottonrat.png)",
              "![](rodent_pictures/Rodent_silhouettes/20-HispidCottonRat.png)",
              "![](rodent_pictures/Rodent_silhouettes/21-Yellownosedcottonrat.png)"), 
